\documentclass[]{article}

\usepackage{soul}
\usepackage[]{listing}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mdframed}
\usepackage[]{color}
\usepackage[]{cancel}

%opening
\title{Pesto Pasta}
\author{A Journey}
\date{}

\definecolor{grey}{rgb}{0.8,0.8,0.8}

\begin{document}

\maketitle

{\large Ingredients}
\begin{itemize}
	\item Spaghetti, raw
	\item Pesto cubes, frozen
	\item Parmesan cheese, fresh
	\item Olive oil, succulent
	\item Salt, possibly
\end{itemize}

\begin{enumerate}
	\item Put $\displaystyle \lim_{x \to 0}\frac{\sin 24x}{\frac{3}{2}x}$ cups of water on the water boiling machine in order to boil the water.
	\item While the water is coming to a boil, defrost $\displaystyle \frac{1}{3}\:\left.\frac{d}{dx}\right|_{x=1}\left(-x^3+3x^2+9x\right)$ cubes of pesto in the microwave and mix with a small amount of olive oil.
	
	\item When the water is rollingly boiling, add $\displaystyle \pi\int_0^{\frac{1}{2}}\cos(\pi t)\:\text{d}t$ pounds of spaghetti.
	
	\begin{mdframed}[hidealllines=true,backgroundcolor=grey]
		Jeremiah has recently won a 100 liter tub of honey from his local fair. He is sad because his jar has started to leak and Jeremiah is slowly losing his most favorite succulent treat. His sadness $t$ days after discovering the leak can be represented by the function $\displaystyle s(t)=\sin\left(\ln\left(10t+1\right)\right)$ for all $t\geq0$. Let $T_s$ be the time (in days) when Jeremiah's sadness is the lowest between $t=0$ and $t=30$ (calculator allowed).
	\end{mdframed}
	
	\item Cook the pasta for $\displaystyle T_s$ minutes, then strain out the pasta.
	
	\pagebreak
	
	\begin{mdframed}[hidealllines=true,backgroundcolor=grey]
		The Gregarious \st{Gooner} Goofball has been \st{gooning} working non-stop for years. He needs a break, and is going on a 7-day all-inclusive stay at the gorgeous Goofy Getaway. He is charged \$1 per meter that he travels while at the resort. His average velocity in meters per day at specific days during his vacation is given in the above table. Using a four-part left Riemann sum from $t=0$ to $t=7$ with the bounds given in the table, approximate the total charge for this vacation, and call this charge $C_g$.
	\end{mdframed}
	
	\begin{table}
		\centering
		\begin{tabular}{|l|l|l|l|l|}
			\hline
			Day              & 0 & 2 & 4   & 6 \\ \hline
			Velocity ($m$/day) & 0.5 & 1 & 0.5 & 0 \\ \hline
		\end{tabular}
	\end{table}
	
	\item Mix in the pesto, $C_g$ tablespoons of olive oil, and add parmesean cheese to taste.
	
	\item If and only if the series $\displaystyle \sum_{n=1}^\infty\frac{\sqrt[n]{n}}{n\ln n}$ converges, also mix in 74 pounds of salt.
	
	\item Serve and possibly enjoy.
\end{enumerate}

\pagebreak\noindent
\begin{enumerate}
	\item$\displaystyle \lim_{x \to 0}\frac{\sin 24x}{\frac{3}{2}x}$
	\vspace*{6cm}
	\item$\displaystyle \frac{1}{3}\:\left.\frac{d}{dx}\right|_{x=1}\left(-x^3+3x^2+9x\right)$
	\vspace*{6cm}
	\item$\displaystyle \pi\int_0^{\frac{1}{2}}\cos(\pi t)\text{d}t$
	
	\pagebreak\noindent
	
	\item Jeremiah has recently won a 100 liter tub of honey from his local fair. He is sad because his jar has started to leak and Jeremiah is slowly losing his most favorite succulent treat. His sadness $t$ days after discovering the leak can be represented by the function $\displaystyle s(t)=\sin\left(\ln\left(10t+1\right)\right)$ for all $t\geq0$. Find the time $t$ (in days) when Jeremiah's sadness is the lowest between $t=0$ and $t=30$ (calculator allowed).
	
	\vspace*{6cm}
	
	\item The Gregarious \st{Gooner} Goofball has been \st{gooning} working non-stop for years. He needs a break, and is going on a 7-day all-inclusive stay at the gorgeous Goofy Getaway. He is charged \$1 per meter that he travels while at the resort. His average velocity in meters per day at specific days during his vacation is given in the table above. Using a four-part left Riemann sum from $t=0$ to $t=7$, approximate the total charge for this vacation.
\end{enumerate}

\begin{table}
	\centering
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		Day              & 0 & 2 & 4   & 6 \\ \hline
		Velocity ($m$/day) & 0.5 & 1 & 0.5 & 0 \\ \hline
	\end{tabular}
\end{table}

\pagebreak\noindent
\begin{enumerate}
	\item$\displaystyle \lim_{x \to 0}\frac{\sin 24x}{\frac{3}{2}x}$
	
	\begin{align*}
		\lim_{x \to 0}\frac{\sin 24x}{\frac{3}{2}x} &= \frac{2}{3}\lim_{x \to 0}\frac{\sin 24x}{x} \\
		&= \frac{2}{3}\underbrace{\lim_{x \to 0}\frac{\sin 24x}{x}}_{24} \\
		&= \frac{2}{3} \cdot 24 \\
		&= \boxed{16}
	\end{align*}
	
	\item$\displaystyle \frac{1}{3}\:\left.\frac{d}{dx}\right|_{x=1}\left(-x^3+3x^2+9x\right)$
	
	\begin{align*}
		\frac{d}{dx}&\left(-x^3+3x^2+9x\right) = -3x^2 + 6x + 9 \\
		&\left.\left(-3x^2 + 6x + 9\right)\right|_{x=1} = -3(1)^2+6(1)+9 = 12 \\
		\frac{1}{3}&\cdot12 = \boxed{4}
	\end{align*}
	
	\item$\displaystyle \pi\int_0^{\frac{1}{2}}\cos(\pi t)\text{d}t$
	
	\begin{align*}
		u&\text{-sub:} \\ \\
		u&=\pi t & du = \pi dt \\ \\
		\pi\int_0^{\frac{1}{2}}\cos({\pi t}){\:\text{d}t} &= \int_0^{\frac{1}{2}}\cos({\pi t}){\:\pi\text{d}t} \\
		\int_0^{\frac{1}{2}}\cos(\underbrace{\pi t}_{u})\underbrace{\pi\text{d}t}_{\text{d}u} &= \int_0^{\frac{1}{2}\pi}\cos(u)\text{d}u \\
		\int_0^{\frac{1}{2}\pi}\cos(u)\text{d}u &= \boxed{1}
	\end{align*}
	
	\pagebreak\noindent
	
	\item Jeremiah has recently won a 100 liter tub of honey from his local fair. He is sad because his jar has started to leak and Jeremiah is slowly losing his most favorite succulent treat. His sadness $t$ days after discovering the leak can be represented by the function $\displaystyle s(t)=\sin\left(\ln\left(10t+1\right)\right)$ for all $t\geq0$. Find the time $t$ (in days) when Jeremiah's sadness is the lowest between $t=0$ and $t=30$ (calculator allowed).
	
	\begin{align*}
		s'(t&)=\:\:\:\:\frac{10 \, \cos\left(\ln\left(10 \, t + 1\right)\right)}{10 \, t + 1} \\
		s'(t)=0 &\Longleftrightarrow \cos\left(\ln\left(10 \, t + 1\right)\right)=0 \\
		&\Longleftrightarrow \ln(10t+1) = \frac{3}{2}\pi \leftarrow \boxed{\text{When $\sin(\theta) = -1$}} \\
		&\Longleftrightarrow 10t+1 = \exp\left(\frac{3}{2}\pi\right) \\
		&\Longleftrightarrow t = \frac{\exp\left(\frac{3}{2}\pi\right)-1}{10} \\
		&\Longleftrightarrow t \approx \boxed{11.032}
	\end{align*}\footnote{In the original equation, it takes a minimum when $\sin(\theta)=-1$, which does not happen at $\displaystyle \theta=\frac{1}{2}\pi$. So, we solve for when $\displaystyle \theta=\frac{3}{2}\pi$ as opposed to the $\displaystyle \frac{1}{2}\pi$ that a traditional algebraic solve would get with $\displaystyle \arccos$ and all that jazz.}
	
	\item The Gregarious \st{Gooner} Goofball has been \st{gooning} working non-stop for years. He needs a break, and is going on a 7-day all-inclusive stay at the gorgeous Goofy Getaway. He is charged \$1 per meter that he travels while at the resort. Let $v(t)$ represent his average velocity in meters per day. Values of $v(t)$ at specific days during his vacation are given in the table above. Using a four-part left Riemann sum from $t=0$ to $t=7$, approximate the total charge for this vacation.
	
	\begin{align*}
		\int_{0}^{7}v(t)\text{d}t &\approx \underbrace{(2)(0.5)}_{1}+\underbrace{(2)(1)}_{2}+\underbrace{(2)(0.5)}_{1}+\underbrace{(1)(0)}_{0} \\
		&\approx 1+2+1+0 \\
		&\approx \boxed{4}
	\end{align*}
\end{enumerate}

\begin{table}
	\centering
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		Day              & 0 & 2 & 4   & 6 \\ \hline
		$v(t)$ ($m$/day) & 0.5 & 1 & 0.5 & 0 \\ \hline
	\end{tabular}
\end{table}

\end{document}
