\documentclass[]{bill}

\usepackage[]{comment}
\usepackage[]{lipsum}

\begin{document}
	\header{2}{A Bill to Ban the Insider Trading of Stocks and Securities by the People of the United States Congress}{H.R. 6767}{Chuck Grassly}{Waterford Model Congress}{2024-25}{
		\whereas{Congresspeople have used their position and superior knowledge to gain about a 10\% advantage when stock trading, unprecedented in the stock market;}
		
		\whereas{whereas some have begun to use their job for personal gain, not to serve their country.}
	}
	
	\title{This is a title}
	
	\section{Section title}{
		\subsection{Subsection title}{
			This bill may be cited as the “BITS act” or the “Ban on Insider Trading of Stocks Act”.
			\paragraph{Para title}{
				This is a paragraph and it is really long and goes onto the next line ghrbjfej
				\subparagraph{Subpara title}{
					This is a subparagraph and it is really long and goes onto the next line ghrbjfej
					\clause{}{
						This is a paragraph and it is really long and goes onto the next line ghrbjfej
					}
					\clause{}{
						THR
					}
					\clause{}{
						THR
					}
					\clause{}{
						THR
					}
					\clause{}{
						THR
					}
					\clause{}{
						THR
					}
					\clause{}{
						THR
					}
					\clause{}{
						THR
					}
				}
			}
		}
	}
	
	\section{}{
		\subsection{}{
			The value of a stock or security shall refer to the current value of the stock or security at the stock exchange from which it was initially acquired.
		}
	}
	
	
	\section{}{
		\subsection{}{
			Congresspeople shall not be able own or trade stocks or securities relating to commodities or companies that they have any form of control or regulation over, or have information regarding future operations or regulation thereof, whether from any committee, subcommittee,  assembly, including the general assembly, or any other official legislative group.
		}
		\subsection{}{
			No one may own or trade stocks or securities using information from a congressperson who has any form of control or regulation over, or has information regarding future operations or regulation thereof, the securities’ company, whether from any committee, subcommittee,  assembly, including the general assembly, or any other legislative group.
		}
		\subsection{}{
			Congresspeople may not advise anyone, family or otherwise, in their stock trading ordeals, private or otherwise, using private information unavailable to the public, obtained from any committee, subcommittee, assembly, including the general assembly, or any other legislative group.
		}
	}
	
	
	\section{}{
		\subsection{}{
			Any congressperson who violates \re{Sec. 3 § a} or \re{Sec. 3 § c} shall be fined equal to the value of their stocks, plus fifty percent, and be forced to relinquish their stocks to a neutral outside entity for thirty percent of their current value.
		}
		\subsection{}{
			Any family members or people in contact with a congressperson who violate \re{Sec. 3 § b} will be forced to relinquish their stocks to a neutral outside entity for fifty percent of their current value and be fined equal to fifty percent the value of their stocks.
		}
	}
	
	
	\section{}{
		\subsection{}{
			This bill shall go into effect 200 days after its passage.
		}
	}
	
\end{document}
